Medical Concept Extraction

### 2012-12-16 paper/paper.tex
more crap on stemmers

\subsubsection{WordNet Lemmatizer}
TODO(SAM):

>>>>

\subsubsection{WordNet Lemmatizer}
TODO(SAM):
Morphology in WordNet uses two types of processes to try to convert the string passed into one that can be found in the WordNet database. There are lists of inflectional endings, based on syntactic category, that can be detached from individual words in an attempt to find a form of the word that is in WordNet. There are also exception list files, one for each syntactic category, in which a search for an inflected form is done. Morphy tries to use these two processes in an intelligent manner to translate the string passed to the base form found in WordNet. Morphy first checks for exceptions, then uses the rules of detachment. The Morphy functions are not independent from WordNet. After each transformation, WordNet is searched for the resulting string in the syntactic category specified.

The Morphy functions are passed a string and a syntactic category. A string is either a single word or a collocation. Since some words, such as axes can have more than one base form (axe and axis ), Morphy works in the following manner. The first time that Morphy is called with a specific string, it returns a base form. For each subsequent call to Morphy made with a NULL string argument, Morphy returns another base form. Whenever Morphy cannot perform a transformation, whether on the first call for a word or subsequent calls, NULL is returned. A transformation to a valid English string will return NULL if the base form of the string is not in WordNet.
